---
title: "SPM lncRNAs"
author: "Jose Antonio Corona Gomez"
date: "12/4/2022"
output: html_document
---

## Improve the filter to determine which lncRNAs are unique to the tissue

Use the TPM table
1 Generate the average TPM per category and collapse everything into a table
2 to calculate SPM you have to add all the TPM values and divide it by the TPM value of the specific tegido
3 You have to make an accumulation graph and look for the point where 95% of the genes are closest to 0
4 Test for lncRNAs independently of other genes



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tximport)

library(rhdf5)
library(readr)

```


##Read transcriptome and gene tables

####kallisto results needed, Table with transcriptomes and tissue data, abundance values

```{r}

  dir <- "./Quant_result" # add directory where files are located when necessary

  #dir <- "./Quant_result_stranding" # add directory where files are located when necessary

list.files(dir)

tx2gene <- read.csv(file = "tx2gene.csv")

samples <- read.csv(file = "Transcriptomas_A_thaliana_wgcna_usados.csv")
samples
files <- file.path(dir, samples$Run, "abundance.h5")
names(files) <- samples$Run
all(file.exists(files))

  txi <- tximport(files, type = "kallisto", tx2gene = tx2gene)

```

## Generate charts of accounts

```{r}

#head(txi$counts)
names(txi)
#head(txi$countsFromAbundance)
#txi
Cuentas <- txi$counts
Abundance <- txi$abundance
Length <- txi$alength
```
## Create TPM Table



```{r}
rpk <- txi$counts / txi$length
scale_factor <- sum(rpk) / 1e6
tpm <- rpk / scale_factor

write.csv(Cuentas, file = "KallistoExpr.csv", row.names = TRUE)
```
## Gene filter with a number greater than 2 TPM this was taken from Julca et al. 2020

```{r}
#tpm largue matrix
tpm <- as.data.frame(tpm)


tpm<-tpm[rowSums(tpm[,-1])>0, ]

tpm_tissue<-tpm

c=0
for(l1 in tissue_list){
  #print (l1)
  c=c+1
  dft<- filter(table_at_wgcna, tissue == l1)
  list_trans<-dft$Run
  listraw<-paste(list_trans, collapse = ',')
  list_trans<-strsplit(listraw, ",")
  list_trans<-unique((unlist(list_trans)))
  #print (c(list_trans))
  if (length(list_trans)>1){
    dft<-tpm[,list_trans]
    tpm_tissue$Mean <- apply(dft,1,mean)
    #print (c(list_trans))
  } else {
    tpm_tissue$Mean <-tpm[,list_trans]
    #print (c(list_trans))
    }
  names(tpm_tissue)[names(tpm_tissue) == "Mean"] <- l1
}
tpm_tissue<-tpm_tissue[,225:248]

tpm_tissue$TOTAL <-rowSums( tpm_tissue)

```
## Calculate SPM values by tissue

```{r}
library(scales)
spm_tissue <-tpm_tissue
spm_tissue <-tpm_tissue/tpm_tissue$TOTAL
spm_tissue$TOTAL <- NULL
#head (spm_tissue)
## make a density plot
spm_tissue_s <-stack(spm_tissue)

#spm_tissue_s
spm_tissue_s<-na.omit(spm_tissue_s)
#spm_tissue_s<-spm_tissue_s%>% filter(values > 0)
x<-nrow(spm_tissue_s)-nrow(spm_tissue_s)/20 #number of tissues

spm_tissue_s<-spm_tissue_s%>% arrange(values)

x<-spm_tissue_s[x,1]
print(x)
#tail(spm_tissue_s)
#x
#ggplot(spm_tissue_s, aes(x=values)) + geom_density()
den <- ggplot(spm_tissue_s, aes(x=values, after_stat(count))) + 
  geom_density(color= "blue", fill= "lightblue",alpha=0.6)+
  geom_vline(xintercept = x,colour = "red")+
  scale_y_log10() +
  #scale_y_continuous(name = "Average Gbases",limits = c(-0, 22.5),breaks = seq(from = 0.0, to = 30, by = 10))+
  #scale_fill_brewer(palette="Set2")+
  theme(axis.line = element_line(size=1, colour = "black"),
        legend.position="bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title=element_text(size = 12),
        text=element_text(size = 12),
        axis.text.x=element_text(colour="black", size = 12, angle = 0),
        axis.text.y=element_text(colour="black", size = 12))
#den +  annotation_logticks()
den <- ggplotly(den)
den

```


 
 
 

